---
title: "PW1"
output: html_document
date: '2022-09-15'
---

#Partie 1

Question1
```{r}
library("caTools")
```
Loads the package caTools

Question2
```{r}
dataset<-read.csv(file="C:/Users/Pierr/OneDrive/Bureau/Pôle Léonard de Vinci/ESILV/S7/Machine Learning/PW/dataset.csv")
```
Loads the dataset

Question3
```{r}
View(dataset)
```
Views the loaded dataset

Question4
```{r}
dataset$Age=ifelse(is.na(dataset$Age),
                   mean(dataset$Age, na.rm=TRUE),
                   dataset$Age)

dataset$Salary=ifelse(is.na(dataset$Salary),
                   mean(dataset$Salary, na.rm=TRUE),
                   dataset$Salary)
```
Allows missing values to be replaced by the average of the other values

Question5
```{r}
dataset$Country=factor(dataset$Country,
                       levels=c('France','Spain','Germany'),
                       labels=c(1.0,2.0,3.0)
                       )
```
Allows country names (string) to be replaced by doubles to facilitate processing

Question6
```{r}
dataset$Purchased=factor(dataset$Purchased,
                         levels=c('No ','Yes'),
                         labels=c(0,1)
                         )


```
Does the same as the last question but with int (0,1)

Question7
```{r}
library("caTools")
set.seed(123) 
split=sample.split(dataset$Purchased,SplitRatio=0.8)
training_set=subset(dataset,split==TRUE)
test_set=subset(dataset==FALSE)


training_set
```
Allows to separate the dataset in 2 parts: training set and test set, with a separation ratio of 80% for training set and 20% for test set

Question8
```{r}
training_set[,2:3]=scale(training_set[,2:3])
test_set[,2:3]=scale(test_set[,2:3])

View(training_set)
View(test_set)
```
Allows to scale the both dataset then we can work on it and views them


#First machine learning project

Question 1
```{r}
data(iris)
dataset2<-iris
View(iris)
```
Loads the dataset "iris" from R.studio and views it

```{r}
dim(dataset2)
```
Gives us the dimension of the dataset

Question 2
```{r}
library(caret)
validation_index=createDataPartition(dataset2$Species,p = 0.8, list = FALSE) 
validation=dataset2[-validation_index,]
dataset2=dataset2[validation_index,]

dim(dataset2) 
```
Loads the "caret" package and split the dataset into 2 parts: training set and validation set but with another way than before
Shows the dimension of the dataset

Question 3
```{r}
sapply(dataset2,class) 

summary(dataset2) 

levels(dataset2$Species) 

head(dataset2)
```
Allows to apply the function "class" to the dataset (sapply())
Summarizes the main informations of the dataset (summary())
Returns the levels value of the dataset's species (levels())
Shows the head of the dataset (head())

Question 5
```{r}
x<-dataset2[,1:4]
y<-dataset2[,5]

par(mfrow=c(1,4))
  for(i in 1:4){
    boxplot(x[,i], main=names(iris)[i])
  }

```
Plots the boxplots of the different variables
x are the variables (lenghts...) and y is the different species

Question 6
```{r}
plot(y)
```
Plots the number of the different individuals

Question 7
```{r}
featurePlot(x=x,y=y,plot="ellipse")

featurePlot(x=x,y=y,plot="box")
```
Shows the matrix correlation between the different variables
The second plot shows the boxplots of the variables depending on the species

Question 8
```{r}
control<-trainControl(method="cv",number=10) 
metric<-"Accuracy"
```
Controls the computational nuances of the train function with the "cv" method

Question 9

#Model KNN
```{r}
set.seed(123)
fit.knn<-train(Species~. , data=dataset2, method="knn", metric=metric, trControl=control)
print(fit.knn)
```
Sets up a grid with different informations for different models (here: KNN) and measure the "fit" of the model

#Model Support Vector Machines
```{r}
set.seed(123)
fit.svm<-train(Species~. , data=dataset2, method="svmLinear", metric=metric, trControl=control)
print(fit.svm)
```
Sets up a grid for the "SVMLinear" model

#Model Random Forest
```{r}
set.seed(123)
fit.rf<-train(Species~. , data=dataset2, method="rf", metric=metric, trControl=control)
print(fit.rf)
```
Sets up a grid for the "RF" model

Question 10
```{r}
results <- resamples(list(knn=fit.knn, svm=fit.svm, rf=fit.rf))
summary(results)
```
Gives us the results of the differents models

Question 11
```{r}
dotplot(results)
```
Plots the last results

Question 12
```{r}
predictions <- predict(fit.knn, validation)
confusionMatrix(predictions, validation$Species)
```
Predicts the values based on the data from validation
Shows the correlation matrix between the predictions and the validation set


